\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

% Formatting
\pagestyle{empty}
\setlist{nosep, leftmargin=*}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

% Section formatting
\titleformat{\section}{\Large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[:]
\titlespacing{\section}{0pt}{12pt}{6pt}

\begin{document}

% Header
\begin{center}
{\huge \textbf{Subhadip Mitra}}\\[4pt]
\textit{Engineering Leader \& AI Systems Architect}\\[8pt]
Singapore $|$ +65 82501776 $|$ contact@subhadipmitra.com \\
LinkedIn: linkedin.com/in/subhadip-mitra $|$ GitHub: github.com/bassrehab
\end{center}

\begin{flushright}
\small\textit{Last updated: \today}
\end{flushright}

\section{Professional Summary}
Senior Engineering Leader with 15+ years of experience bridging fundamental AI research and enterprise-scale system delivery. Currently leading Google Cloud's Data \& Analytics practice for Southeast Asia while driving internal innovations on LLM inference efficiency and multi-agent systems. Proven track record of operating as a ''Player-Coach'': managing regional engineering portfolios while simultaneously architecting and patenting novel frameworks (UPIR, ARTEMIS, FTCS, Speculative Decoding).

\section{Professional Experience}

\subsection{Google Cloud - Professional Services Organization}
\textbf{Data \& Analytics Manager | Site Lead, PSO Southeast Asia} \hfill \textit{January 2021 -- Present}

Dual-track role combining technical innovation leadership with regional delivery management. Built Google Cloud's Data Analytics practice across Southeast Asia while serving as Site Lead overseeing cross-practice operations. Member of delta - Google Cloud's innovation and transformation team architecting enterprise AI solutions at scale.

\textbf{Strategic Leadership \& Delivery:}
\begin{itemize}
\item Built Data Analytics practice for Southeast Asia from 0 to 1, establishing the region's premier capability serving 7 countries with strategic enterprise clients.
\item Serve as Site Lead overseeing PSO Southeast Asia delivery operations, directing cross-functional teams while maintaining 97\% CSAT and contributing to 100\% annual revenue target attainment.
\item Direct \$XXM+ Data Analytics delivery portfolio across JAPAC while simultaneously overseeing \$XXM+ cross-practice portfolio as regional Site Lead.
\item Led critical engagements for JAPAC strategic accounts including major financial services institutions and consumer electronics manufacturers, ensuring delivery excellence and client success.
\item Executed high-impact projects including 12K+ user analytics migrations, first Data \& AI Centers of Excellence, Data Monetization Platforms, and petabyte-scale data platform modernizations.
\item Partner with C-level stakeholders (CTOs, CDOs) to define data modernization and AI transformation roadmaps, translating technical capabilities into business outcomes.
\item Pioneered organization-wide adoption of agentic AI across PSO JAPAC for both customer solutions and internal productivity, including autonomous data engineering agents.
\end{itemize}

\textbf{Technical Innovation \& Research (Official IP):}
\begin{itemize}
\item Research on speculative decoding, custom Triton kernels, and KV-cache compression strategies. Filed Google Technical Disclosure on hybrid compression systems for multi-tenant serving optimization.
\item Invented neuro-symbolic framework combining formal verification and reinforcement learning to automate distributed system generation - achieved 274x speedup in synthesis with 60\% latency reduction.
\item Designed Field-Theoretic Context System modeling context as continuous fields to address long-horizon memory fragmentation in AI agents. Published as Google Technical Disclosure.
\item Authored whitepaper introducing Extract, Transform, Load, Contextualize framework adding semantic, relational, and behavioral context to data pipelines for RAG and agentic systems.
\item Created adaptive debate-driven decision framework for enterprise multi-agent systems. Published as Google Technical Disclosure.
\item Developed industry-agnostic agentic AI system for enterprise-scale trust decisions across Finance, Healthcare, Insurance, Cybersecurity, and Supply Chain. Features APLS (self-learning pattern synthesis) and five-level cascade routing achieving 86\% cost reduction with sub-50ms latency. Won Google Cloud PSO Hackathon JAPAC Regionals, qualified for World Finals. Two pending Google Technical Disclosures.
\end{itemize}

\subsection{Standard Chartered Bank}
\textbf{Principal Engineer - Data \& Analytics Transformation} \hfill \textit{January 2019 -- January 2021}

Led enterprise-wide AI and data platform development serving 11 markets and 1200+ global users, delivering technical excellence while influencing C-suite data strategy.

\begin{itemize}
\item Delivered a Self-Service ML Platform that reduced model development time from 6 months to 1 week
\item Designed credit risk AI models integrating alternative data sources, improving accuracy by 15\%
\item Modernized MarTech infrastructure, driving 30\% increase in customer acquisition
\end{itemize}

\subsection{Think Big Analytics (a Teradata company)}
\textbf{Principal Data Engineer / Solution Architect} \hfill \textit{January 2017 -- January 2019}

Architected enterprise-scale data solutions for Fortune 500 clients across APAC, designing scalable platforms with measurable business impact.

\begin{itemize}
\item Engineered 5 high-performance data lakes processing 1.2 PB/hour, achieving 20\% optimization
\item Built real-time fraud detection systems, reducing false positives by 60\% and saving \$XM annually
\item Designed enterprise architectures supporting global Fortune 500 clients across APAC
\end{itemize}

\subsection{Various Companies}
\textbf{Software Engineering, Architecture and Technical Consulting Roles} \hfill \textit{January 2010 -- January 2017}

Progressively advanced through roles in software development, systems integration, and technical consulting within financial services and algorithmic trading domains.

\section{Research \& Open Source Engineering}

\textbf{LLM Inference Efficiency Research} \\
Research implementations addressing the fundamental bottleneck in LLM inference: memory-bandwidth constraints rather than compute limits. Explores acceleration through speculative decoding, custom GPU kernels, and quantization strategies. \\
GitHub: \url{https://github.com/bassrehab/speculative-decoding} $|$ GitHub: \url{https://github.com/bassrehab/triton-kernels}
\\
\textit{Google Technical Disclosure - Pending}

\textbf{AI Metacognition Toolkit} \\
Activation-level detection of sandbagging, deception, and situational awareness in LLMs. Linear probes achieve 90-96\% accuracy across Mistral, Gemma, and Qwen models. Includes steering vectors for runtime behavior control. \\
PyPI: \url{https://pypi.org/project/ai-metacognition-toolkit/} $|$ GitHub: \url{https://github.com/bassrehab/ai-metacognition-toolkit} $|$ Docs: \url{https://ai-metacognition-toolkit.subhadipmitra.com/} $|$ \url{/blog/2025/detecting-ai-sandbagging/}

\textbf{UPIR - Distributed Systems Synthesis} \\
Neuro-symbolic framework combining formal verification, program synthesis, and reinforcement learning to automatically generate verified distributed system implementations from specifications. \\
\url{https://www.tdcommons.org/dpubs_series/8852/} $|$ GitHub: \url{https://github.com/bassrehab/upir}

\textbf{Steering Vectors for Agent Behavior Control} \\
Runtime control of LLM agent behaviors through activation steering vectors - modifying model outputs at inference time without retraining. Demonstrates more calibrated control than traditional prompting approaches with LangChain integration. \\
GitHub: \url{https://github.com/bassrehab/steering-vectors-agents} $|$ \url{/blog/2025/steering-vectors-agents/}

\textbf{Spark LLM Eval - Distributed Evaluation Framework} \\
Distributed LLM evaluation framework built on Apache Spark for enterprise-scale model assessment. Addresses the gap in evaluating LLMs at scale with statistical rigor, integrating seamlessly with Databricks infrastructure. \\
GitHub: \url{https://github.com/bassrehab/spark-llm-eval} $|$ \url{/blog/2025/building-spark-llm-eval/}

\textbf{CatchMe - Intelligent Trust Engine} \\
Industry-agnostic agentic AI system for enterprise-scale trust decisions across Finance, Healthcare, Insurance, Cybersecurity, and Supply Chain. Uses adversarial debate protocols (prosecutor/defense/judge) to filter hallucinations and build audit trails for regulated environments. \\
\\
\textit{Google Technical Disclosures - Pending (APLS \& Cascade Routing)}

\section{Publications \& Technical Disclosures}

\textbf{UPIR: Automated Synthesis and Verification of Distributed Systems} \\
\textit{Google, Technical Disclosure Commons, November 2025} \\
\url{https://www.tdcommons.org/dpubs_series/8852/}

\textbf{ETLC: A Context-First Approach to Data Processing in the Generative AI Era} \\
\textit{Google Cloud, May 2025} \\
\url{https://services.google.com/fh/files/blogs/etlc_full_paper.pdf}

\textbf{Field-Theoretic Context System (FTCS)} \\
\textit{Google, Technical Disclosure Commons, May 2025} \\
\url{https://www.tdcommons.org/dpubs_series/8022/}

\textbf{ARTEMIS - Adaptive Multi-agent Debate Framework} \\
\textit{Google, Technical Disclosure Commons, January 2025} \\
\url{https://www.tdcommons.org/dpubs_series/7729/}

\textbf{Data Monetization Strategy for Enterprises} \\
\textit{BITS Pilani, December 2023} \\
\url{https://www.researchgate.net/publication/376557741_Data_Monetization_Strategy_for_Enterprises}

\textbf{OConsent: Open Consent Protocol for Privacy and Consent Management with Blockchain} \\
\textit{BITS Pilani, December 2021} \\
\url{https://arxiv.org/abs/2201.01326}

\section{Education}

\textbf{MBA, Business Analytics} \hfill Birla Institute of Technology and Science, Pilani
\textbf{MTech, Software Systems} \hfill Birla Institute of Technology and Science, Pilani

\section{Technical Skills}

\subsection{Technology Leadership \& Strategy} Enterprise Architecture, Technical Vision \& Roadmaps, Digital Transformation, AI \& Data Strategy, Cloud Architecture, C-Suite Advisory, Innovation Leadership, Strategic Planning

\subsection{Data Engineering \& Architecture} Petabyte-Scale Data Platforms, Data Pipelines, Real-Time Processing, Data Mesh \& Fabric, Apache Spark, Apache Hadoop, Apache HBase, Apache Flink, Apache Kafka, Apache Iceberg

\subsection{Generative AI \& Machine Learning} Multi-Agent Systems, Large Language Models, RAG Architecture, Vector Databases, PyTorch, LangChain, LangGraph, LlamaIndex, Google ADK, MCP, A2A Protocol, MLflow, LLMOps

\subsection{Cloud Platforms \& Infrastructure} Google Cloud Platform, BigQuery, Vertex AI, Dataflow, Cloud Composer, GKE, Terraform, Kubernetes

\subsection{Programming \& Development} Python, SQL, Scala, Triton, CUDA, Algorithm Design, Formal Verification, Program Synthesis, Distributed Systems

\section{Professional Affiliations}

IEEE • ACM • Singapore Computer Society • Royal Institute of Navigation • IIT Madras

\end{document}