\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

% Formatting
\pagestyle{empty}
\setlist{nosep, leftmargin=*}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

% Section formatting
\titleformat{\section}{\Large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[:]
\titlespacing{\section}{0pt}{12pt}{6pt}

\begin{document}

% Header
\begin{center}
{\huge \textbf{Subhadip Mitra}}\\[4pt]
\textit{Engineering Leader \& AI Systems Architect}\\[8pt]
Singapore $|$ +65 82501776 $|$ contact@subhadipmitra.com \\
LinkedIn: linkedin.com/in/subhadip-mitra $|$ GitHub: github.com/bassrehab
\end{center}

\begin{flushright}
\small\textit{Last updated: \today}
\end{flushright}

\section{Professional Summary}
Senior Engineering Leader with 15+ years bridging AI research and enterprise delivery. Leading Google Cloud's Data \& Analytics practice for Southeast Asia while driving innovations in LLM inference and multi-agent systems. Track record as ''Player-Coach'' - managing regional portfolios while architecting patented frameworks (UPIR, ARTEMIS, FTCS).

\section{Professional Experience}

\subsection{Google Cloud - Professional Services Organization}
\textbf{Data \& Analytics Manager | Site Lead, PSO Southeast Asia} \hfill \textit{January 2021 -- Present}

Built Google Cloud's Data Analytics practice across Southeast Asia. Dual role as Site Lead overseeing regional delivery and technical innovation lead on delta team.

\begin{itemize}
\item Built D\&A practice from 0 to 1 serving 7 countries; direct \$XXM+ portfolio with 97\% CSAT
\item Led strategic interventions for JAPAC accounts including major FSI and electronics manufacturers
\item Delivered 12K+ user migrations, Data \& AI CoEs, and petabyte-scale platform modernizations
\item Published 5 technical disclosures (UPIR, FTCS, ARTEMIS, ETLC, CatchMe) on AI/distributed systems
\item Won Google Cloud PSO Hackathon JAPAC for CatchMe intelligent trust engine
\end{itemize}

\subsection{Standard Chartered Bank}
\textbf{Principal Engineer - Data \& Analytics Transformation} \hfill \textit{January 2019 -- January 2021}

Led enterprise AI and data platform development serving 11 markets and 1200+ users.

\begin{itemize}
\item Delivered Self-Service ML Platform reducing model development from 6 months to 1 week
\item Designed credit risk AI models improving accuracy by 15\% with alternative data sources
\item Modernized MarTech infrastructure driving 30\% increase in customer acquisition
\end{itemize}

\subsection{Think Big Analytics (Teradata)}
\textbf{Principal Data Engineer / Solution Architect} \hfill \textit{January 2017 -- January 2019}

Architected enterprise data solutions for Fortune 500 clients across APAC.

\begin{itemize}
\item Engineered 5 data lakes processing 1.2 PB/hour with 20\% optimization
\item Built real-time fraud detection reducing false positives by 60\%
\end{itemize}

\subsection{Various Companies}
\textbf{Software Engineering \& Technical Consulting} \hfill \textit{January 2010 -- January 2017}

Progressive roles in software development, systems integration, and consulting in financial services and algorithmic trading.

\section{Research \& Open Source Engineering}

\textbf{LLM Inference Efficiency} \\
Speculative decoding, custom Triton kernels, KV-cache compression. 8.1x speedup, 88\% peak bandwidth on A100. \\
GitHub: \url{https://github.com/bassrehab/speculative-decoding}
\\
\textit{Google Technical Disclosure - Pending}

\textbf{AI Metacognition Toolkit} \\
Activation-level detection of sandbagging and deception in LLMs. 90-96\% accuracy with steering vectors. \\
PyPI: \url{https://pypi.org/project/ai-metacognition-toolkit/}

\textbf{UPIR - Distributed Systems Synthesis} \\
Neuro-symbolic framework for automated distributed system generation. 274x speedup, 60\% latency reduction. \\
\url{https://www.tdcommons.org/dpubs_series/8852/}

\textbf{CatchMe - Intelligent Trust Engine} \\
Agentic AI for enterprise trust decisions. APLS pattern learning + cascade routing. 86\% cost reduction, sub-50ms latency. JAPAC Hackathon Winner. \\
\\
\textit{Google Technical Disclosures - Pending}

\section{Publications \& Technical Disclosures}

\textbf{UPIR: Automated Synthesis and Verification of Distributed Systems} \\
\textit{Google, Technical Disclosure Commons, November 2025} \\
\url{https://www.tdcommons.org/dpubs_series/8852/}

\textbf{ETLC: Context-First Data Processing for GenAI} \\
\textit{Google Cloud, May 2025} \\
\url{https://services.google.com/fh/files/blogs/etlc_full_paper.pdf}

\textbf{Field-Theoretic Context System (FTCS)} \\
\textit{Google, Technical Disclosure Commons, May 2025} \\
\url{https://www.tdcommons.org/dpubs_series/8022/}

\textbf{ARTEMIS - Adaptive Multi-agent Debate Framework} \\
\textit{Google, Technical Disclosure Commons, January 2025} \\
\url{https://www.tdcommons.org/dpubs_series/7729/}

\textbf{OConsent: Blockchain Privacy \& Consent Protocol} \\
\textit{BITS Pilani / arXiv, December 2021} \\
\url{https://arxiv.org/abs/2201.01326}

\section{Education}

\textbf{MBA, Business Analytics} \hfill BITS Pilani
\textbf{MTech, Software Systems} \hfill BITS Pilani

\section{Technical Skills}

\subsection{Leadership} Enterprise Architecture, Digital Transformation, AI \& Data Strategy, C-Suite Advisory

\subsection{Data \& AI} Petabyte-Scale Platforms, Apache Spark/Kafka/Flink, LLMs \& Multi-Agent Systems, RAG \& Vector Databases, PyTorch, Vertex AI

\subsection{Cloud \& Engineering} Google Cloud Platform, BigQuery, Python/SQL/Scala, Kubernetes, Distributed Systems

\section{Professional Affiliations}

IEEE • ACM • Singapore Computer Society

\end{document}